### 2013-06-11 Tex/chapters/model.tex
kleinere Korrekturen
Unnötige Klammer, falsche Jahreszahl
nur Notizen

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{sec:graphtypes}
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}.
    \begin{figure}[htbp]
        \centering
        %~ \subfigure{\input{GG_def}}
        %~ \subfigure{\input{RNG_def}}
        \subfigure{\input{images/GG_RNG_def}}
        \subfigure{\includegraphics[width=0.3\textwidth]{images/GGL12S03.pdf}}
        \subfigure{\includegraphics[width=0.3\textwidth]{images/RNGL12S03.pdf}}
        \caption[Definition of the lunes and examples of the Gabriel
                and Relative Neighborhood Graph]
                {Left: Lunes of Gabriel Graph (red) and Relative
                    Neighborhood Graph (blue and red). Middle:
                    Example of a Gabriel Graph. Periodic nodes are
                    dashed. Right: Example of a Relative
                    Neighborhood Graph. Periodic nodes are dashed.}
        \label{fig:lunes}
    \end{figure}

@@

\subsection{Critical Temperature $T_c$ and Critical Exponents}
    Because the searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    [vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{Newman1998} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
    die exponenten reproduziert hat].\\
    Though if one is just interested in the critical Temperature an
    easier approach is to find the intersections of the binder cumulants
    \(g = \brac{3-\frac{\avg{m^4}}{2\avg{m^2}^2}}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
    the intersection. %[vgl. Grafik (villeicht)]
    The arithmetic average of the intersections are plotted [hier schon?]
    %~ [Und den rest der Auswertung]
    \\

>>>>

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{sec:graphtypes}
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}.
    \begin{figure}[htbp]
        \centering
        \subfigure{\input{images/GG_RNG_def}}
        \subfigure{\includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}}
        \subfigure{\includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}}
        \caption[Definition of the lunes and examples of the Gabriel
                and Relative Neighborhood Graph]
                {Left: Lunes of Gabriel Graph (red) and Relative
                    Neighborhood Graph (blue and red). Middle:
                    Example of a Gabriel Graph. Periodic nodes are
                    dashed. Right: Example of a Relative
                    Neighborhood Graph. Periodic nodes are dashed.}
        \label{fig:lunes}
    \end{figure}

@@

\subsection{Critical Temperature $T_c$ and Critical Exponents}
    Because the searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    [vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{Newman1998} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    Though if one is just interested in the critical Temperature an
    easier approach is to find the intersections of the binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
    the intersection. %[vgl. Grafik (villeicht)]
    The arithmetic average of the intersections are plotted [hier schon?]
    %~ [Und den rest der Auswertung]
    \\

% Erwahnen, dass T_c Graph so aussieht, wie degree graph
% mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
% cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52
